master thesis

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Version 4
Paper - Results - Biological View

      \begin{table} [h]
        \begin{center}
          \begin{tabular}{ |l|r|r||r|r|r| }
            \hline
            Domain  & \% unknown states & \% multifurcation \\ 
            / Kingdom  & (missing state information & (missing \\
            / Phylum / Class & of leaf nodes) & internal nodes) \\
            \hline \hline
            Eukaryota       & 97.34~\%  & 98.16~\% \\
            \hline \hline
            Metazoa         & 96.44~\%  & 87.93~\% \\ \hline
            Fungi           & 98.87~\%  & 96.97~\% \\ \hline
            Chloroplastida  & 99.14~\%  & 89.46~\% \\
            \hline \hline            
            Arthropoda      & 97.49~\%  & 89.95~\% \\ \hline
            Apicomplexa     & 86.26~\%  & 87.16~\% \\ \hline
            Nematoda        & 89.01~\%  & 88.59~\% \\ \hline
            Chordata        & 88.59~\%  & \cellcolor{green!50}66.49~\% \\ \hline
            Platyhelminthes & \cellcolor{green!50}68.73~\%  & 80.34~\% \\
            \hline \hline            
            Insecta         & 97.11~\%  & 90.78~\% \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Examination of subtrees regarding missing information}
        \label{table:percentage loss information subtrees} 
      \end{table}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of castor}

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Biological view}

      \todo{Castor replaces originaltags with finaltags. There are 82 originaltags != finaltag.} \\

      We picked a few phyla to evaluate the results from the biological point of view. \\
      Table \ref{table:phylum leaf nodes states} shows some known phyla: Chordata, Nematoda, 
        Platyhelminthes and Apicomplexa. \\
      Since GloBI is not perfect, all examples contain a few bugs.

      \todo{\ref{table:table:percentage loss information subtrees}} \\

      As known the Chordata are full of free-living species and there are only a few parasites. Among 
        the birds are some breeding parasites (brood parasitism) like the cuckoo and clepto-parasites as 
        the skuas \cite{Rothschild1957}. The algorithm reflects this. We started with 99.83~\% 
        free-living species and predicted 99.94~\% species as parasites \todo{(inklusive all known nodes)}. 
        Only 0.06~\% were predicted as parasites. \\
      \todo{We found the cuckoo and some skuas...?} \\
      Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95~\% as 
        parasites. \\
      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
        \todo{ref einfügen}. But at the end we predicted 4.18~\% as free-living. The class Seriata is the 
        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
        the prediction looks right. \\
        \todotext{ Wiki: \\
        *The Seriata are an order of turbellarian flatworms.[1][2] \\
        They are found in both freshwater and marine environments, and also include a number of species 
        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
        from other related groups by the presence of a folded pharynx and of a number of diverticula 
        arising from the intestine. The intestine itself may be either simple or branched.[3]}

      With the Nematoda it looks very different. In the Nematoda its much worse. Most Nematoda are 
        free-living, but we found only 2.63~\% of them. Blaxter et al. speaks of at least seven 
        independently arosed parasitism \cite{Blaxter1998}. In a recent article Blaxter identifies 18 
        origins \cite{Blaxter2015} in Nematoda. \\
        The problem at this point, however, is obvious: The parasites have been much more studied and 
        thus we start with only 0.63~\% free-living species. Against such a shifted data situation, the 
        algorithm is almost powerless. And yet the percentage has increased.

        The evolution of parasitism in Nematoda: \\
        "while only approximately 23 000 species have been described (J. Hallan, unpublished; https://insects.tamu.edu/research/collection/hallan/), the true species-level diversity may be 1 million or more (Lambshead, 1993)." \\
        " Estimates of the number of species of parasitic nematode per host suggest that there may be of the order of 25 000 nematode parasites just of vertebrates, most of which remain undescribed (Dobson et al. 2008)" \\
        "a large proportion of nematode species may be parasites." \cite{Blaxter2015} \\

      \begin{table}
        \begin{center}
          \hspace*{-1cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{original states} & \multicolumn{6}{c|}{final states} \\
            Phylum & \# nodes & FL & P
              & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            \hline \hline
            Chordata & 91785 & 10451 & 18 
              & 91734 & 0 & 0 & 0 & 0 & 51 \\
            & & 99.83~\% & 0.49~\%
              & 99.94~\% & & & & & 0.06~\% \\ \hline
            Nematoda & 30127 & 21 & 3289 
              & 791 & 0 & 1017 & 0 & 0 & 28319 \\
            & & 0.63~\% & 99.37~\%
              & 2.63~\% & & 3.38~\% & & & 94~\% \\ \hline
            Platyhelminthes & 22683 & 7 & 7086 
              & 949 & 0 & 151 & 0 & 0 & 21583 \\
            & & 0.1~\% & 99.9~\%
              & 4.18~\% & & 0.67~\% & & & 95.15~\% \\ \hline
            Apicomplexa & 1863 & 1 & 255 
              & 1 & 0 & 0 & 0 & 0 & 1862 \\
            & & 0.39~\% & 99.61~\%
              & 0.05~\% & & & & & 99.95~\% \\
            \hline \hline
            Arthropoda & 1198981 & 18912 & 11141 
              & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
            & & 62.93~\% & 37.07~\%
              & 91.7~\% & 0.11~\% & 1.87~\% & 0.35~\% & 0.14~\% & 5.86~\% \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Phylum (leaf nodes)}
        \label{table:phylum leaf nodes states} 
      \end{table}

      \anmerkungstext{Das sind schonmal vier große Kontraste, wenn dann noch Zeit bleibt, die 
        schwirigen... Arthropoden, Fungi, Pflanzen... (Emanuel)} \\

      \begin{table}
        \begin{center}
          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
            Kingdom & \# nodes & FL & P
              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            \hline \hline
            none & 84456 & 45 & 529 
              & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
            Fungi & 324105 & 577 & 2983
              & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
            Chloroplastida & 460457 & 3519 & 77
              & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
            Metazoa & 1670956 & 30758 & 22373
              & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Kingdom (inkl internal nodes)}
      \end{table}

      \begin{table}
        \begin{center}
          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{original states} & \multicolumn{6}{c|}{final states} \\
            Phylum & \# nodes & FL & P
              & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            \hline \hline
            Chordata & 122546 & 10451 & 18 
              & 122473 & 0 & 0 & 0 & 0 & 73 \\
            Nematoda & 33564 & 21 & 3289 
              & 846 & 0 & 1133 & 0 & 0 & 31585 \\
            Platyhelminthes & 27142 & 7 & 7086 
              & 1010 & 0 & 175 & 0 & 0 & 25957 \\
            Apicomplexa & 2102 & 1 & 255 
              & 1 & 0 & 0 & 0 & 0 & 2101 \\
            \hline
            Arthropoda & 1319460 & 18912 & 11141 
              & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
            \hline
          \end{tabular}
        \end{center}
        \caption{Phylum (inkl internal nodes)}
      \end{table}

      \begin{table}
        \begin{center}
          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
            Kingdom & \# nodes & FL & P
              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            \hline \hline
            none & 75446 & 45 & 529 
              & 13426 & 220 & 24082 & 0 & 7792 & 5302 & 0 & 24493 \\
            Fungi & 31457 & 577 & 2983
              & 38520 & 0 & 0 & 0 & 5723 & 0 & 0 & 266463 \\
            Chloroplastida & 416478 & 3519 & 77
              & 410795 & 0 & 0 & 0 & 4182 & 0 & 0 & 1501 \\
            Metazoa & 1491012 & 30758 & 22373
              & 1328135 & 0 & 0 & 930 & 25535 & 4423 & 1665 & 130324 \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Kingdom (leaf nodes)}
      \end{table}

@@

  Fehlerqoute der Daten an sich? \\
  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit 
  Information. \\
  Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
  Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
  Es gibt noch ungenutze information in GloBI.

>>>>

      \begin{table} [h]
        \begin{center}
          \begin{tabular}{ |l|r|r||r|r|r| }
            \hline
            Domain  & \% unknown states & \% multifurcation \\ 
            / Kingdom  & (missing state information & (missing \\
            / Phylum / Class & of leaf nodes) & internal nodes) \\
            \hline \hline
            Eukaryota       & 97.34~\%  & 98.16~\% \\
            \hline \hline
            Metazoa         & 96.44~\%  & 87.93~\% \\ \hline
            Fungi           & 98.87~\%  & 96.97~\% \\ \hline
            Chloroplastida  & 99.14~\%  & 89.46~\% \\
            \hline \hline            
            % Arthropoda      & 97.49~\%  & 89.95~\% \\ \hline
            Apicomplexa     & 86.26~\%  & 87.16~\% \\ \hline
            Nematoda        & 89.01~\%  & 88.59~\% \\ \hline
            Chordata        & 88.59~\%  & \cellcolor{green!50}66.49~\% \\ \hline
            Platyhelminthes & \cellcolor{green!50}68.73~\%  & 80.34~\% \\
            \hline \hline            
            Insecta         & 97.11~\%  & 90.78~\% \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Examination of subtrees regarding missing information}
        \label{table:percentage loss information subtrees} 
      \end{table}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of the real data analysis created with Sankoff}

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Biological view}
      To analyze the results, we have selected some phyla (sub-trees) to evaluate our results 
        selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
        Apicomplexa. \\
      In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
      There are several factors that play a role here, and in part, crystallize in these examples. \\
      An important factor here is that the credibility of the results with the accuracy of the input 
        data, i. the data of GloBI, stands and falls. Errors of incorrect input data can be amplified by 
        incorrect prediction of unknown species and can be reversed in order to improve the data 
        situation of GloBI. \\
      Since we look at such large trees we can not expect to know all the parasites, so we look at 
        individual positives. Positive in the sense that the majority have the opposite state.

      \begin{table}[h]
        \begin{center}
          \begin{tabular}{ |l|r||r|r||r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{original states} & \multicolumn{4}{c|}{final states} \\
            Phylum & \# nodes       & FL & P              & 0 (FL) & 0.3 & 0.5 & 1 (P) \\
            \hline \hline
            Chordata & 91785        & 10451 & 18          & 91759 & 0 & 0 & 26 \\
            &                       & 99.83~\% & 0.49~\%  & 99.97~\% & & & 0.03~\% \\ \hline
            Nematoda & 30127        & 21 & 3289           & 1604 & 142 & 1196 & 27185 \\
            &                       & 0.63~\% & 99.37~\%  & 5.32~\% & 0.47~\% & 3.97~\% & 90.23~\% \\ \hline
            Platyhelminthes & 22683 & 7 & 7086            & 175 & & & 22508 \\
            &                       & 0.1~\% & 99.9~\%    & 0.77~\% & 0 & 0 & 99.23~\% \\ \hline
            Apicomplexa & 1863      & 1 & 255             & 1 & 0 & 0 & 1862 \\
            &                       & 0.39~\% & 99.61~\%  & 0.05~\% & & & 99.95~\% \\
            % \hline \hline
            % Phylum & \# nodes & FL & P
            %   & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            % Arthropoda & 1198981 & 18912 & 11141 
            %   & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
            % & & 62.93~\% & 37.07~\%
            %   & 91.7~\% & 0.11~\% & 1.87~\% & 0.35~\% & 0.14~\% & 5.86~\% \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Phylum (leaf nodes)}
        \label{table:phylum leaf nodes states} 
      \end{table}

      In contrast to the other phyla examined, the phylogeny is more pronounced (less multifurcation) (see 
        Table \ref{table:table:percentage loss information subtrees}). This results in a weaker spread of 
        errors. This is reflected in the results from the table \ref{table:phylum leaf nodes states}. 
        There are 18 parasites as input data and only 8 more are predicted. The chordata mostly consist of 
        free-living species, so this seems believable. We started with 99.83~\%  species and 
        predict 99.97~\% species as free-living (including already known nodes). 
        \todo{A few punctual tests give us the following:}

      \begin{figure}[h!]
        \centering
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.85\textwidth]{Figures/ChordataParasites.png}
        \caption{Parasites of Phylum: Chordata}
        \label{fig:ChordataParasites}
      \end{figure}

      We mapped the few parasitic spezies in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
      Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
        got 6 input parasites from GloBI and there are no predictions: A woodpecker - Sphyrapicus varius
        and a duck - Aix sponsa, a cow bird - Molothrus ater known as broodparasite and some others. \\
        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
        % Snake: Storeria dekayi (probably caused by wrong input data.)
      % \begin{itemize}
      %   \item Order Cypriniformes (7): carp-type without family.
      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
      %     they eat fin or pieces of larger fish.
      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
      %     species in here.
      % \end{itemize}
      % For the Chordata as parasitic species were predicted in the following orders and families:
      % \begin{itemize}
      %   \item Order Cypriniformes (16), nine predicted parasites.
      %   \item Order Sauria (6), only given input parasites.
      %   \item Order Acanthomorphata(3), only given input parasites.
      %   \item Order Anura (1), only given input parasite.
      %   \item Order Siluriformes (1), only given input parasites.
      % \end{itemize}

      The Apicomplexa are a parasitic phylum. We found only one input organism: Stemonitis fusca as a 
        free-living specie. In GloBI it is listed as being parasitized by Nectria candicans and Nectriopsis 
        sporangiicola\footnote{
          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=parasiteOf&targetTaxon=Stemonitis\%20fusca}
          {https://www.globalbioticinteractions.org/?interactionType=parasiteOf\&targetTaxon=Stemonitis\%20fusca}
        }. The algorithm has not predicted new free-livings. \\

      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
        \todo{ref einfügen}. But at the end we predicted 0.1~\% as free-living. The class Seriata is the 
        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
        the prediction looks right. \\
        \todotext{ Wiki: \\
        *The Seriata are an order of turbellarian flatworms.[1][2] \\
        They are found in both freshwater and marine environments, and also include a number of species 
        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
        from other related groups by the presence of a folded pharynx and of a number of diverticula 
        arising from the intestine. The intestine itself may be either simple or branched.[3]} \\
      Note:Plythylmintes had less missing information than starting point, see Table \ref{table:percentage loss information subtrees}.

      With the Nematoda it looks very different. In the Nematoda its much worse. Large parts of Nematoda 
        are free-living, but we found only 5.32~\% of them. Blaxter et al. speaks of at least seven 
        independently arosed parasitism \cite{Blaxter1998}. In a recent article Blaxter identifies 18 
        origins \cite{Blaxter2015} in Nematoda. \\
        The problem at this point, however, is obvious: The parasites have been much more studied and 
        thus we start with only 0.63~\% free-living species. Against such a shifted data situation, the 
        algorithm is almost powerless. And yet the percentage has increased.

      \todo{The evolution of parasitism in Nematoda:} \\
      "while only approximately 23 000 species have been described (J. Hallan, unpublished; https://insects.tamu.edu/research/collection/hallan/), the true species-level diversity may be 1 million or more (Lambshead, 1993)." \\
      " Estimates of the number of species of parasitic nematode per host suggest that there may be of the order of 25 000 nematode parasites just of vertebrates, most of which remain undescribed (Dobson et al. 2008)" \\
      "a large proportion of nematode species may be parasites." \cite{Blaxter2015} \\

      % \anmerkungstext{Das sind schonmal vier große Kontraste, wenn dann noch Zeit bleibt, die 
      %   schwirigen... Arthropoden, Fungi, Pflanzen... (Emanuel)} \\

      \todotext{Im Folgenden folgen 3 weitere ähnliche tabellen. Einmal eine ähnliche Tabelle inklusive 
        interner Knoten \ref{table:Phylum internal nodes}, zweimal die Übersicht über die Kingdoms 
        Blattknoten \ref{table:Kingdom leaf nodes} bzw interne Knoten \ref{table:Kingdom internal nodes}. Welche 
        nehmen wir? Rest Appendix oder ganz raus?}

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{original states} & \multicolumn{6}{c|}{final states} \\
            Phylum & \# nodes & FL & P
              & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            \hline \hline
            Chordata & 122546 & 10451 & 18 
              & 122473 & 0 & 0 & 0 & 0 & 73 \\
            Nematoda & 33564 & 21 & 3289 
              & 846 & 0 & 1133 & 0 & 0 & 31585 \\
            Platyhelminthes & 27142 & 7 & 7086 
              & 1010 & 0 & 175 & 0 & 0 & 25957 \\
            Apicomplexa & 2102 & 1 & 255 
              & 1 & 0 & 0 & 0 & 0 & 2101 \\
            % \hline
            % Arthropoda & 1319460 & 18912 & 11141 
            %   & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
            \hline
          \end{tabular}
        \end{center}
        \caption{Phylum (inkl internal nodes)}
        \label{table:Phylum internal nodes}
      \end{table}

      \begin{table}
        \begin{center}
          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
            Kingdom & \# nodes & FL & P
              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            \hline \hline
            none & 75446 & 45 & 529 
              & 13426 & 220 & 24082 & 0 & 7792 & 5302 & 0 & 24493 \\
            Fungi & 31457 & 577 & 2983
              & 38520 & 0 & 0 & 0 & 5723 & 0 & 0 & 266463 \\
            Chloroplastida & 416478 & 3519 & 77
              & 410795 & 0 & 0 & 0 & 4182 & 0 & 0 & 1501 \\
            Metazoa & 1491012 & 30758 & 22373
              & 1328135 & 0 & 0 & 930 & 25535 & 4423 & 1665 & 130324 \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Kingdom (leaf nodes)}
        \label{table:Kingdom leaf nodes}
      \end{table}

      \begin{table}
        \begin{center}
          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{original states} & \multicolumn{8}{c|}{final states} \\
            Kingdom & \# nodes & FL & P
              & 0 (FL) & 0.25 & 0.33 & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            \hline \hline
            none & 84456 & 45 & 529 
              & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
            Fungi & 324105 & 577 & 2983
              & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
            Chloroplastida & 460457 & 3519 & 77
              & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
            Metazoa & 1670956 & 30758 & 22373
              & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Kingdom (inkl internal nodes)}
        \label{table:Kingdom internal nodes}
      \end{table}

@@

  Fehlerqoute der Daten an sich? \\
  Wie gut ist unsere Datenlage? 3 mio knoten, 1.8 named species (leaf nodes), 200.000 leaf nodes mit 
  Information. \\
  Welche Teile des Baumes sind gut, an welchen muss noch viel geforscht werden. \\
  Wieviele Origins haben wir gefunden, was bedeutet diese Zahl? \\
  Es gibt noch ungenutze information in GloBI. \\
  Wir können GloBI verbessern ... Wir haben GloBI auf die gefundenen Abweichungen aufmerksam gemacht... 
    Fehler werden durch die prediction eventuell verstärkt...\\
